\documentclass{article}

\usepackage[french,english]{babel}
\usepackage{eurosym}
\usepackage{iflang}
\usepackage{resume}

% define some colors
\usepackage{xcolor}
\definecolor{highlight}{HTML}{283559}
\definecolor{link}{HTML}{0A66C2} % light blue
% coloring of links
\usepackage[
	colorlinks = true,
	urlcolor = link,
	%linkcolor = link,
	%citecolor= highlight
]{hyperref}
%\usepackage{hyperref}
\usepackage{fontawesome5}

% Adjust margins
%\iffalse
\iftrue
\addtolength{\topmargin}{-2.0cm} % top margin
\addtolength{\textheight}{2.0cm} % bottom margin
\addtolength{\oddsidemargin}{-2.0cm} % left margin
\addtolength{\textwidth}{4.0cm} % right margin
\fi

\newcommand{\colorLinkedinSign}
{\textcolor{rgb:red,6;green,108;blue,170}{\faLinkedinSign}}

\begin{document}
\selectlanguage{english}
\name{\bf Corentin LE MOLGAT}
\vspace{-0.80cm}
\href{mailto:corentin.lemolgat@gmail.com}{\texttt{corentin.lemolgat@gmail.com}}\\
T\'{e}l: +33 6 66 89 42 07\\
\faLinkedin~\href{https://www.linkedin.com/in/corentin-le-molgat-a957893b/}{\texttt{Corentin Le Molgat}}
\faGithub~\href{https://github.com/Mizux}{\texttt{Mizux}}\\
\IfLanguageName{english} {
Japanese spouse visa holder\\
} {
}
\vspace{-0.80cm}
\begin{llist}
% Working Experience
\IfLanguageName{english} {
\sectiontitle{Work Experience}
} {
\sectiontitle{Exp\'{e}rience Professionnelle}
}
\vspace{-0.60cm}
\IfLanguageName{english} {
\employer{Adecco, Contractor at Google LLC}
} {
\employer{Adecco, CDD \`{a} Google LLC}
}
\location{Paris, France}
\dates{01/2020--01/2021}

\vspace{-0.60cm}
\IfLanguageName{english} {
\employer{Kelly Services, Contractor at Google LLC}
} {
\employer{Kelly Services, CDD \`{a} Google LLC}
}
\location{Paris, France}
\dates{11/2017--05/2019}
\IfLanguageName{english} {
Open Source Software Release Manager\\
Optimization Team:
\vspace{-0.50cm}
\begin{itemize}
	\item Released several versions of
    \href{https://github.com/google/or-tools}{\texttt{Google OR-Tools}} (PyPI, Nuget, GitHub).
	\item Reworked and maintained the
    \href{https://developers.google.com/optimization/}{\texttt{online documentation}}
    (HTML, markdown, doxygen).
	\item Provided support to customer (GitHub issues, Stack Overflow).
	\item Developed and maintained few samples (C++, Java, Python, .Net).
	\item Maintained the Makefile based build system (Makefile, bash).
	\item Maintained the Bazel based build system (Bazel).
	\item Developed and maintained the CMake based build system (CMake).
	\item Developed and maintained a public CI system (Travis CI, Appveyor, Docker).
	\item Provided training \& support for CMake.
\end{itemize}
} {
Open Source Software Release Manager\\
Equipe Optimization:
\vspace{-0.50cm}
\begin{itemize}
	\item Publication de plusieurs versions de
		\href{https://github.com/google/or-tools}{\texttt{Google OR-Tools}} (PyPI, Nuget, GitHub).
  \item Refonte et maintenance de la
    \href{https://developers.google.com/optimization/}{\texttt{documention en ligne}}
    (HTML, markdown, doxygen).
  \item Support propos\'{e} aux utilisateurs (GitHub issues, Stack Overflow).
  \item D\'{e}veloppement et maintenance de plusieurs examples (C++, Java, Python, .Net).
  \item Maintenance du syst\`{e}me de build utilisant Makefile (Makefile, bash).
  \item Maintenance du syst\`{e}me de build utilisant Bazel (Bazel).
  \item D\'{e}veloppement et maintenance du syst\`{e}me de build utilisant CMake (CMake).
  \item D\'{e}veloppement et maintenance du syst\`{e}me d'int\'{e}gration continue publique (Travis CI, Appveyor, Docker).
  \item Formation \& support apport\'{e} sur CMake.
\end{itemize}
}

\employer{Aldebaran Robotics/SoftBank Robotics Europe}\location{Paris, France}
\dates{04/2012--11/2017}
\IfLanguageName{english} {
Embedded System \& Computer Vision Software Engineer \\
System Team:
\vspace{-0.50cm}
\begin{itemize}
	\item Developed and maintained a Kernel Linux SoC Driver (C, MT9M114, OV5640).
	\item Developed a camera firmware flasher (Archlinux \& Yocto, C++).
	\item Managed a contractor for an UVC compliant firmware (CMake, Docker, C++, Catch, GTest, Plantuml).
\end{itemize}
Vision Team:
\vspace{-0.50cm}
\begin{itemize}
	\item Reworked and maintained a C++ framework for multi-client access to robot cameras (CMake, C++, Boost).
	\item Developed tooling for a camera viewer (C++, Qt).
	\item Developed Modularity, a C++ computational graph framework for perception.
	\item Maintained the internal CI builfarm, testing and training (Jenkins,
		gcovr).
	\item Provided training \& support for CMake and C++ as a senior developer.
\end{itemize}
Misc:
\vspace{-0.50cm}
\begin{itemize}
	\item Supported the vision system for the R\&D team and research partners.
	\item Provided support on the production line, Yantai (China), 1 month.
\end{itemize}
} {
R\&D Ing\'{e}nieur Informaticien Vision par Ordinateur et Syst\`{e}me
embarqu\'{e} \\
Equipe Syst\`{e}me:
\vspace{-0.50cm}
\begin{itemize}
	\item D\'{e}veloppement et maintenance d'un driver SoC pour un noyau Linux (C, MT9M114, OV5640).
	\item D\'{e}veloppement d'un chargeur de micrologiciel (firmware) pour une cam\'{e}ra (Archlinux \& Yocto, C++).
	\item Gestion d'un fournisseur pour un micrologiciel compatible UVC (CMake, Docker, C++, Catch, GTest, Plantuml).
\end{itemize}
Equipe Vision:
\vspace{-0.50cm}
\begin{itemize}
	\item Refonte et maintenance d'un framework C++ pour l'acc\`{e}s multi-clients aux cam\'{e}ras du robot (CMake, C++, Boost).
	\item D\'{e}velopement d'outils de visualisation pour cameras (C++, Qt).
	\item D\'{e}velopement de Modularity, un framework C++ de graph de calcul pour Perception.
	\item Maintenance d'une builfarm d'int\`{e}gration continue interne, test et formation (Jenkins, gcovr).
	\item Formation \& support sur CMake et C++ en tant que d\'{e}veloppeur s\'{e}nior.
\end{itemize}
Divers:
\vspace{-0.50cm}
\begin{itemize}
	\item Support et formation sur l'utilisation du syst\`{e}me de vision pour l'\'{e}quipe de R\&D et les partenaires de recherche.
	\item Support sur la ligne de production, Yantai (Chine), 1 mois.
\end{itemize}
}

\employer{Vi Technology}\location{St-Egr\`{e}ve, France}
\dates{02/2010--12/2011}
\IfLanguageName{english} {
R\&D GPGPU and Vision System Software Engineer\\
Responsible for the design and development of the whole acquisition and processing pipeline
for a new AOI (Automated Optical Inspection) system for SPI (Solder Past Inspection)
 running on Linux (Fedora).\\
% Hardware
Software lead for the hardware acquisition system integration (Vertex-6 Card on PCIe):
\vspace{-0.50cm}
\begin{itemize}
	\item Managed the integration of the FPGA.
	\item Defined the protocol between the Kernel and the acquisition card.
	\item Developed the Kernel device driver (C).
	\item Developed debugger tools (C++, Qt).
\end{itemize}
% Software
Software lead on the image pipeline:
\vspace{-0.50cm}
\begin{itemize}
	\item Developed a C++ middleware to grab and manage images from several dozens of image sensors.
	\item Managed two co-workers to speed up development (roadmap, code review, scrum master).
	\item Developed a 2D camera image viewer (C++, Qt, OpenSceneGraph).
\end{itemize}
% GPGPU
Software lead on the GPGPU post-processing pipeline:
\vspace{-0.50cm}
\begin{itemize}
	\item Ported the 3D reconstruction algorithm (Matlab) to a dual-GPU System (CMake, C++, CUDA 4, GTX 480)
		and speed it up from 15s to 7ms (x2000!).
	\item Developed a CMake cross toolchain for managing CUDA files.
	\item Developed a 3D PCB viewer (after 3D reconstruction) using (C++, Qt, OpenSceneGraph).
\end{itemize}
Various support as technical lead on GNU/Linux:
\vspace{-0.50cm}
\begin{itemize}
	\item CMake training \& support.
	\item Jenkins training \& support (PoC, setup, design).
	\item Linux training \& support (Bash, Fedora) (everyone else was on Windows).
\end{itemize}
} {
R\&D Ing\'{e}nieur Informaticien Syst\`{e}me de Vision et GPGPU\\
%\vspace{-0.50cm}
Responsable de l'architecture et du d\'{e}veloppement de l'ensemble de la chaine d'acquisition et de traitement
pour une nouvelle machine d'AOI (Automated Optical Inspection) pour l'\'{e}tape de SPI (Solder Past Inspection)
tournant sous GNU/Linux (Fedora).\\
% Hardware
Software lead pour l'int\'{e}gration du syst\`{e}me d'acquisition mat\'{e}riel (Vertex-6 Card on PCIe):
\vspace{-0.50cm}
\begin{itemize}
	\item Gestion de l'int\'{e}gration du FPGA.
	\item D\'{e}finition du protocole entre le noyau Linux et la carte d'acquisition.
	\item D\'{e}veloppement du pilote de p\'{e}riph\'{e}rique du noyau (C).
	\item D\'{e}veloppement d'un outils de d\'{e}bogage (C++, Qt).
\end{itemize}
% Software
Software lead sur le pipeline d'image:
\vspace{-0.50cm}
\begin{itemize}
	\item D\'{e}veloppement d'un middleware d'acquisition et de gestion des
		images depuis deux douzaines de capteurs CMOS (C++).
	\item Gestion de deux co-workers pour acc\'{e}l\'{e}rer le d\'{e}veloppement (roadmap, code review, scrum master).
	\item D\'{e}veloppement d'un visualiseur d'image de cam\'{e}ra 2D (C++, Qt, OpenSceneGraph).
\end{itemize}
% GPGPU
Software lead sur le pipeline de post-processing GPGPU:
\vspace{-0.50cm}
\begin{itemize}
	\item Portage de l'agorithme de reconstruction 3D (Matlab) vers un syst\`{e}me bi-GPU (CMake, C++, CUDA 4, GTX 480)
		et acc\'{e}l\'{e}ration de 15s \`{a} 7ms (x2000!).
	\item D\'{e}veloppement d'une cross toolchain CMake pour g\'{e}rer les fichiers CUDA.
	\item D\'{e}veloppement d'un visualiseur 3D de PCB apr\'{e}s reconstruction 3D (C++, Qt, OpenSceneGraph).
\end{itemize}
Supports divers commme responsable technique sur GNU/Linux:
\vspace{-0.50cm}
\begin{itemize}
	\item CMake formation \& support.
	\item Jenkins formation \& support (PoC, setup, design).
	\item Linux formation \& support (Bash, Fedora) (tout le monde \'{e}taient sur Windows).
\end{itemize}
}

% Internship
\employer{Kyushu University}\location{Fukuoka, Japan}
\dates{04/2009--10/2009}
\IfLanguageName{english} {
Engineering intern at I.R.V.S. (laboratory for Intelligent Robots \& Vision System)
\vspace{-0.50cm}
\begin{itemize}
	\item Design (UML) and implementation (C++) of a
		3D human pose estimation using non-parametric belief propagation
		algorithms and multiple 2D video cameras.
	\item Developed a tooling viewer (C++, Qt, OpenSceneGraph).
\end{itemize}
} {
Stage d'ing\'{e}nieur \`{a} l'I.R.V.S. (laboratory For Intelligent Robots \& Vision System)
\vspace{-0.50cm}
\begin{itemize}
	\item Conception (UML) et impl\'{e}mentation (C++) d'un algorithme
		d'estimation de pose humaine en 3D par propagation de croyance
		non-param\'{e}trique \`{a} partir plusieurs flux vid\'{e}o de cam\'{e}ras 2D.
	\item D\'{e}veloppement d'une application de visualisation (C++, Qt, OpenSceneGraph).
\end{itemize}
}

% Internship
\employer{Kyushu University}\location{Fukuoka, Japan}
\dates{06/2008--09/2008}
\IfLanguageName{english} {
Engineering intern at I.R.V.S. (laboratory For Intelligent Robots \& Vision System)
\vspace{-0.50cm}
\begin{itemize}
	\item 3D Reconstruction on GPU (GLSL) using stereovision algorithms and four 2D video cameras.
	\item Developed a tooling viewer (C++, Qt).
\end{itemize}
} {
Stage d'ing\'{e}nieur \`{a} l'I.R.V.S. (laboratory For Intelligent Robots \& Vision System)
\vspace{-0.50cm}
\begin{itemize}
	\item Reconstruction 3D d'une sc\`{e}ne sur GPU (GLSL) utilisant un algorithme
		de st\'{e}r\'{e}ovision et 4 cam\'{e}ras monochromes.
	\item D\'{e}veloppement d'une application de visualisation (C++, Qt).
\end{itemize}
}

\sectiontitle{Education}
\employer{ENSEIRB} \location{Bordeaux, France}
\dates{09/2006--10/2009}
\IfLanguageName{english} {
B.S./M.S. in Computer Science with a specialty in HPC (High Performance Computing).
} {
Dipl\^{o}me d'ing\'{e}nieur en Informatique option PRCD (Parall\'{e}lisme,
R\'{e}gulation et Calcul Distribu\'{e}).
}

% Skills
\IfLanguageName{english} {
\sectiontitle{Skills}
{\em Competence}: Programming, CI, Documentation, Tooling, Image Pipeline, Drivers, Robotics \\
{\em Programming Languages}: Bash, Kernel C, C++, Python, Java, .Net, Docker \\
{\em Programming Libraries}: STL, OpenCV, Boost, V4L2, ffmpeg \\
{\em Extra Interests}: Android, Vulkan, Spir V \\
{\em Languages}: French (native), English (fluent), Japanese (beginner), Spanish (beginner) \\
} {
\sectiontitle{Comp\'{e}tences}
{\em Comp\'{e}tences}: Programmation, CI, Documentation, Outillage, Drivers, Vision, Robotique \\
{\em Langages de Programmation}: Kernel C, C++, Bash, Python, Java, .Net, Docker \\
{\em Biblioth\`{e}ques Logicielles}: STL, Qt, OpenCV, Boost, V4L2, ffmpeg \\
{\em Autres Int\'{e}r\^{e}ts}: Android, Vulkan, Spir V \\
{\em Langues}: Fran\c{c}ais (natif), Anglais (fluent), Espagnol (d\'{e}butant), Japonais (d\'{e}butant) \\
}

% References
\IfLanguageName{english} {
\sectiontitle{References}
} {
\sectiontitle{R\'{e}f\'{e}rences}
}
\input{references.tex}
\end{llist}

{\em Last update: \today}

\end{document}
